Dataset-level report

### 2019-11-15 analysis/reports/dat_report_template.Rmd
add title to fs plot

fs_heatmap <- ggplot(data = fs_samples, aes(x = rank, y = abund, group = sim, color = source)) +
  geom_line(alpha = .01) +
  geom_line(data = filter(fs_samples, source == "observed")) +
  theme_bw() +
  scale_color_viridis_d(end = .8)

>>>>

fs_heatmap <- ggplot(data = fs_samples, aes(x = rank, y = abund, group = sim, color = source)) +
  geom_line(alpha = .01) +
  geom_line(data = filter(fs_samples, source == "observed")) +
  theme_bw() +
  scale_color_viridis_d(end = .8) +
  ggtitle(a_fs_name)
